Proposed Solution

### 2016-01-28 design.tex
we are not complete over ordering!

>>>>

There is actually a bit of a catch in ordering though - we are not complete over ordering rules.
This is because only our implementation does not satisfy the specification for the merge function listed above.
The problem arises from the fact the configuration files may have non-unique keywords.
Therefor, in the follwoing file we will derive the valid, but conflicting rules ([client],port) and (port,[client]).
\begin{verbatim}
[client]
port = 3306
[mysqld]
port = 3306
\end{verbatim}
Our implementation of merge removes and conflicting rules for the running set.
By introducing a renaming pass in the initial parsing we may be able to solve this, but have not found a satisfactory solution yet.
